---
title: "Regression"
output:
  word_document: default
  html_document:
    df_print: paged
---
# Intoduction

This is about regression, we are about to perform regression analysis using marketing data of the datarium package in r. 

# Data 

The marketing data has 200 observations and 4 variables namely: youtube, facebook, newspaper, and sales.

```{r echo=FALSE}
# Inspect the data
sample_n(marketing, 3)
```


```{r echo=FALSE, results='hide'}
summary(marketing$youtube)
summary(marketing$facebook)
summary(marketing$newspaper)
summary(marketing$sales)
```


```{r echo=FALSE, results='hide'}
```


```{r echo=FALSE, results='hide'}
library(tidyverse)
library("caret")
theme_set(theme_bw())
```

```{r}
# Load the data
data("marketing", package = "datarium")
# Inspect the data
sample_n(marketing, 3
```






```
```{r}
# Split the data into training and test set
set.seed(123)
training.samples <- marketing$sales %>%
  createDataPartition(p = 0.8, list = FALSE)
train.data  <- marketing[training.samples, ]
test.data <- marketing[-training.samples, ]
```
```{r}
# Build the model
model <- lm(sales ~., data = train.data)
# Summarize the model
summary(model)
# Make predictions
predictions <- model %>% predict(test.data)
# Model performance
# (a) Prediction error, RMSE
RMSE(predictions, test.data$sales)
# (b) R-square
R2(predictions, test.data$sales)
```

```{r}
# Predicting with new data 
# using the model
youtube <- 0
facebook <- 90
newspaper <- 0
a <- data.frame(youtube, facebook, newspaper)
p <- model %>%predict(a)
p
```

Our model is as follows 
$$\hat{y} = 3.59 + 0.04x_1 + 0.19X_2 + \epsilon$$
where $\hat{y}is sales, and $x_2$ id youtube, $x_2$ is facebook, and $\epsilon$ is the error term. 

```{r}
model <- lm(sales ~ youtube, data = train.data)
summary(model)$coef
```

```
```{r}

```


